Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-16 code/analysis.Rmd
done with monte carlo figure for now

@@

@@

@@

for (i in 1:nrow(skeleton_eta)) {
  monte[[i]] <- tibble(phi = skeleton_eta$phi[i],
                       Re = skeleton_eta$Re[i],
                       eta = rnorm(1000, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
}

@@

Grouped by Re:

@@

monte2 <- list()

for (i in 1:nrow(skeleton_eta)) {
  monte2[[i]] <- tibble(phi = skeleton_eta$phi[i],
                       Re = skeleton_eta$Re[i],
                       eta = rnorm(1000, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
}

lmsre <- bind_rows(monte2) %>%
  mutate(ID = paste0(Re, 1:1000)) %>%
  lmList(log(eta) ~ phi|ID, data = .) %>%
  coefficients()

lmsre <- lmsre %>%
  group_by(Re) %>%
  summarise(avg = mean(phi, na.rm = TRUE), sd = sd(phi, na.rm = TRUE)) %>%
  mutate(ymax = avg + 1.96*sd)

lmsre %>%
  ggplot(aes(x = as.numeric(Re), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  theme_bw()

>>>>

lm(data = c_over_phi, formula = log10(C) ~ log10(phi)) %>% summary()

@@

Models:

@@

library(cowplot)

reps = 10000

@@

monte <- list()
for (i in 1:nrow(skeleton_eta)) {
  monte[[i]] <- tibble(phi = skeleton_eta$phi[i],
                       Re = skeleton_eta$Re[i],
                       eta = rnorm(reps, mean = skeleton_eta$eta[i], sd = skeleton_eta$deta[i]))
}
lmsphi <- bind_rows(monte) %>%
  mutate(ID = paste0(phi, 1:reps),
         logRe = log(Re)) %>%
  lmList(log(eta) ~ logRe|ID, data = .) %>%
  coefficients()
lmsphi <- tibble(phi = str_sub(rownames(lmsphi),0,6),lmsphi)
lmsphi <- lmsphi %>%
  group_by(phi) %>%
  summarise(avg = mean(logRe, na.rm = TRUE), sd = sd(logRe, na.rm = TRUE)) %>%
  mutate(ymax = avg + 1.96*sd)
lmsphi

lmsre <- bind_rows(monte) %>%
  mutate(ID = paste0(Re, 1:reps),
         logphi = log(phi)) %>%
  lmList(log(eta) ~ logphi|ID, data = .) %>%
  coefficients()

lmsre <- lmsre %>%
  group_by(Re) %>%
  summarise(avg = mean(logphi, na.rm = TRUE), sd = sd(logphi, na.rm = TRUE)) %>%
  mutate(ymax = avg + 1.96*sd)

@@

Plots:

@@

p_phi <- lmsphi %>%
  ggplot(aes(x = paste0(100*as.numeric(phi),"%"), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  ylim(-3,1.5) +
  xlab(expression(paste("Solid volume fraction (",phi,")"))) +
  ylab(expression(paste("Effect size: ",beta[log(Re)])))

p_re <- lmsre %>%
  ggplot(aes(x = as.factor(round(as.numeric(Re),0)), y = avg, ymin = avg-1.96*sd, ymax = avg+1.96*sd)) +
  geom_point() +
  geom_errorbar() +
  theme_bw() +
  ylim(-3,1.5) +
  xlab(expression(Re[c])) +
  ylab(expression(paste("Effect size: ",beta[log(phi)])))

plot_grid(p_re, p_phi, labels = c("(a)","(b)"), scale = .9)
